# DNAPlotR

[![Build Status](https://travis-ci.org/sherrillmix/identiconr.svg?branch=master)](https://travis-ci.org/sherrillmix/identiconr)
[![codecov.io](https://codecov.io/github/sherrillmix/identiconr/coverage.svg?branch=master)](https://codecov.io/github/sherrillmix/identiconr?branch=master)

##Install
An R library to generate random identicon patterns. To install directly from github, use the [<code>devtools</code>](https://github.com/hadley/devtools) library and run:

```{r, eval=FALSE}
devtools::install_github("sherrillmix/identiconr")
```
Then load the library as normal using:
```{r}
library(dnaplotr)
```

## Main functions
### generateIdenticon 
<code>generateIdenticon(seqs)</code> takes an integer or character seed and generates a corresponding assortment of shapes and colors. For example:

```{r seqExample,tidy=TRUE,results='hide'}
generateIdenticon('test@email.com')
```

This isn't particularly useful by itself but will usually be used with the following function.

### plotIdenticon
<code>plotIdenticon(seqs)</code> takes the output from <code>generateIdenticon</code> (or a seed directly) and plots them to the current device. For example:

```{r aaExample,tidy=TRUE,results='hide'}
plotIdenticon(generateIdenticon('test@email.com'))
plotIdenticon(seed='abc')
```

See [doc/example.pdf](the vignette) for complete plotting details.

