# identiconr

```{r, echo=FALSE}
set.seed(1234)
```


## Install

An R library to generate random identicon patterns. To install directly from github, use the [<code>devtools</code>](https://github.com/hadley/devtools) library and run:

devtools::install_github("sherrillmix/identiconr")
```{r, eval=FALSE}
devtools::install_github("sherrillmix/identiconr")
```
Then load the library as normal using:
```{r}
library(identiconr)
```

## Main functions
### plotIdenticon

<code>plotIdenticon(seqs)</code> takes the output from <code>generateIdenticon</code> (or a seed directly) and plots them to the current device. For example:

```{r identiconExample,tidy=TRUE,results='hide'}
plotIdenticon(generateIdenticon('test@email.com'))
plotIdenticon(seed='abc')
plotIdenticon(seed='abc',col='red',back='blue')
plotIdenticon(seed='abc',nSquare=3)
plotIdenticon(seed='abc',nSquare=5)
```

```{r manyIdenticon,tidy=TRUE,results='hide',fig.width=9,fig.height=4.5}
par(mfrow=c(10,20),mar=rep(.1,4))
for(ii in 1:200)plotIdenticon(nSquare=3)
```


### generateIdenticon 

<code>generateIdenticon(seqs)</code> takes an integer or character seed and generates a corresponding assortment of shapes and colors. For example:

```{r generateExample,tidy=TRUE}
generateIdenticon('test@email.com')
```

This isn't particularly useful by itself and will probably only be used with `plotIdenticon()` but is provided for any extensions or manual adjustment.


